Together, Individuals Make a Difference

### 2025-01-27 论文/PAPER.tex
latex

\section{Appendix B: Program Codes}
Here are the program codes we used in our research.

@@

		\subitem\textbf{Query2: }Is there a recommended tennis dataset source that includes detailed information about each serve of a player, such as the first and second hand, score, running distance, and serving posture? CSV format required

		\subitem\textbf{Purpose: }We attempted to inquire with AI about machine learning datasets for tennis matches, and AI provided several related websites. Unfortunately, we ultimately did not find any high-quality data available.

		\subitem\textbf{Output: }As of my knowledge deadline (January 2022), I am unable to provide specific tennis dataset links. However, you can try searching for tennis datasets in the following places:ATP official website: ATP (Association of Tennis Professionals) may provide some official tennis datasets. You can search for relevant statistics and data on its website.The official website of ITF: The International Tennis Federation (ITF) may also provide some tennis datasets. Check their official website to see if there is any information you need.Kaggle: Kaggle is a data science competition platform where users sometimes share various datasets, including sports data. You can search for relevant tennis datasets on Kaggle.UCI Machine Learning Library: UCI machine learning libraries typically provide various types of datasets, including sports related data. You can check their website to see if there is a tennis dataset that suits your needs.GitHub: Some developers and researchers may share their collected tennis datasets on GitHub. You can search on GitHub and see if there are any projects that meet your requirements.Please ensure that you comply with relevant laws and regulations regarding data usage, and review the license agreement for the dataset to ensure that you have the right to use it. Also, remember to check if the dataset contains the specific information you need, such as first and last, score, running distance, and serving posture.
	\end{itemize}
\end{letter}

>>>>

\clearpage
\section{Appendix B: Program Codes}
Here are the program codes we used in our research.

@@

		\subitem\textbf{Query2: }Ways to make the abstract and sections of the paper more concise while maintaining an academic tone.

		\subitem\textbf{Purpose: }We attempted to to refine the abstract and sections of the paper to be more concise, ensuring that the content remains academically rigorous and effectively communicates the research findings, methods, and significance.

		\subitem\textbf{Output: }Focus on the core objectives, methods, results, and implications of the study. Use clear and concise language to summarize the research without unnecessary details.Clearly state the research question or hypothesis and its significance. Avoid extensive background information that does not directly relate to the research focus.Methods: Describe the research design and procedures succinctly. Include only essential details that are necessary for replication or understanding of the study. Results: Present findings in a straightforward manner, emphasizing key outcomes. Avoid repetitive explanations of data that are self-evident from the figures or tables.Discussion: Concentrate on interpreting the results and their implications. Avoid speculative or tangential discussions that do not directly relate to the study's findings.Conclusion: Summarize the main findings and their significance concisely. Avoid restating information already covered in the abstract or introduction.Example: Before: "We performed data preprocessing and feature engineering on the provided dataset, using the KMeans++ clustering algorithm to determine the ranking of each country."After: "We preprocessed data using KMeans++ to rank countries."
	\end{itemize}
\end{letter}
